### 2019-12-09 ch1_introduction/content.tex
remove usage of particular commands

\begin{figure}[htb!]
	\centering
	\includegraphics[width=\LARgefigure]{fig/bulk_vs_sc} 
	\caption{
		\textbf{The 'masking' effect of bulk omics.} 
		\textbf{A:} Cells from several subpopulations are incorrectly assumed to be homogeneous and are profiled with a single bulk omics experiment.
		\textbf{B:} The signals from the different subpopulations are masked. The resulting profile is dissimilar from the majority of cells it is supposed to represent.
	}
	\label{fig:bulk_vs_sc}
\end{figure}

@@

\section{Computational tools}
Whole-genome profiling at single-cell level allows new types of analyses with which to study cellular heterogeneity at a hitherto unseen throughput. 
The new types of analyses permitted by single-cell omics present several computational challenges \cite{stegle_computationalanalyticalchallenges_2015, yuan_challengesemergingdirections_2017, chen_singlecellrnaseqtechnologies_2019}. This necessitates the development of novel computational tools, either because the problem statement of the performed analysis is completely novel, or to adapt existing methodology to new data characteristics -- dimensionality and noise.

>>>>

\begin{figure}[htb!]
	\centering
	\includegraphics[width=0.6\textwidth]{fig/bulk_vs_sc} 
	\caption{
		\textbf{The 'masking' effect of bulk omics.} 
		\textbf{A:} Cells from several subpopulations are incorrectly assumed to be homogeneous and are profiled with a single bulk omics experiment.
		\textbf{B:} The signals from the different subpopulations are masked. The resulting profile is dissimilar from the majority of cells it is supposed to represent.
	}
	\label{fig:bulk_vs_sc}
\end{figure}

@@

\section{Computational tools} \label{sec:comptools}
Whole-genome profiling at single-cell level allows new types of analyses with which to study cellular heterogeneity at a hitherto unseen throughput. 
The new types of analyses permitted by single-cell omics present several computational challenges \cite{stegle_computationalanalyticalchallenges_2015, yuan_challengesemergingdirections_2017, chen_singlecellrnaseqtechnologies_2019}. This necessitates the development of novel computational tools, either because the problem statement of the performed analysis is completely novel, or to adapt existing methodology to new data characteristics -- dimensionality and noise.

### 2019-12-09 ch7_incgraph/content.tex
remove usage of particular commands

%% FIGURE 1
\picfig{fig/figure1.pdf}{\LARGEfigure}{fig_graphlets}{{\bf Graphlet counting in a network characterises its local topologies.}
	(A) In total, there are 30 different graphlets containing 2 to 5 nodes, ranging from $G_0$ to $G_{29}$. Orbits are an extension of graphlets which also take into account the position of a node within a graphlet. The 73 different orbits are coloured in red. (B) By counting the occurrences of these graphlets in the network, the local topology surrounding a node can be quantified.}

@@

%% FIGURE 2
\picfig{fig/figure2.pdf}{.7\linewidth}{fig_efficient}{{\bf Several strategies are employed in order to reduce time and memory consumption.}
(A) Only the depth 3 neighbourhood of each modified edge needs to be explored in order to have visited all modified five-node graphlets. (B) A lookup table can be used to easily look up the graphlet index of a subgraph, by weighing each edge in a 5-node subgraph by a power of~2. (C) The same combination of five nodes is never repeated, as to avoid counting the same graphlet multiple times. (D) The adjacency matrix of the network is compressed in order to reduce memory usage.}

@@

%% FIGURE 3
\picfig{fig/figure3.pdf}{\LARGEfigure}{fig_method_speedup}{{\bf Static network model generators were modified to generate dynamic networks.}
	Three network models were used: Barabási–Albert, Erdős–Rényi, and Geometric. Step 0: a network is generated according to the network model and the given parameters. Step 1: the network is modified such that the result is as likely to have been generated by the network model. Step 2: The time for IncGraph to calculate the differences in graphlet counts is measured ($T_{IG}$). Step 3: The time for the non-incremental approach to calculate the graphlet counts of the new network is measured ($T_{NI}$). Steps 1 to 3 are repeated until all modifications generated at step 0 are processed, or until an execution time threshold has been reached.}

@@

%% FIGURE 4
\picfig{fig/figure4.pdf}{.9\linewidth}{fig_method_reranking}{{\bf Predicted gene regulatory networks of model organisms are optimised to reduce the false positive rate.}
	A)~The number of redundant edges in each graphlet are counted. B) The network is optimised in order to obtain a lower redundancy over time. Two networks are shown, one before and one after the optimisation procedure. Edges coloured in red have been removed from the network after optimisation, green edges have been added. C) Starting from an empty network, the interactions are modified by iteratively evaluating the increase in redundancy of the next $k$ interactions, and adding the first edge for which its redundancy is less than the $90^\textrm{th}$ percentile redundancy.}

@@

%% FIGURE 5
\picfig{fig/figure5.pdf}{\LARGEfigure}{fig_speedup}{{\bf IncGraph is significantly faster than non-incremental approaches.}
	For small networks, the execution time of IncGraph $T_{IG}$ is already 50 times less than that of non-incremental approaches $T_{NI}$. This ratio increases even further for networks with higher numbers of nodes or higher average degrees.}

@@

%% FIGURE 6
\picfig{fig/figure6.png}{\Largefigure}{fig_reranking}{{\bf A simple graphlet-based scoring method improves predicted regulatory networks.}
	(A) The F1 score was calculated by calculating the harmonic mean of the AUROC and AUPR scores of the first 1000 interactions. (B) IncGraph is significantly faster than the non-incremental approach. Note that for each interaction added to the network, the graphlet counts of 100 putative interactions were evaluated.}

>>>>

%% FIGURE 1
\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.8\textwidth]{fig/figure1.pdf}
	\caption{%
		{\bf Graphlet counting in a network characterises its local topologies.}
		(A) In total, there are 30 different graphlets containing 2 to 5 nodes, ranging from $G_0$ to $G_{29}$. Orbits are an extension of graphlets which also take into account the position of a node within a graphlet. The 73 different orbits are coloured in red. (B) By counting the occurrences of these graphlets in the network, the local topology surrounding a node can be quantified.
	}
	\label{fig_graphlets}
\end{figure}

@@

%% FIGURE 2
\begin{figure}[ht!]
	\centering
	\includegraphics[width=.7\linewidth]{fig/figure2.pdf}
	\caption{{\bf Several strategies are employed in order to reduce time and memory consumption.}
		(A) Only the depth 3 neighbourhood of each modified edge needs to be explored in order to have visited all modified five-node graphlets. (B) A lookup table can be used to easily look up the graphlet index of a subgraph, by weighing each edge in a 5-node subgraph by a power of~2. (C) The same combination of five nodes is never repeated, as to avoid counting the same graphlet multiple times. (D) The adjacency matrix of the network is compressed in order to reduce memory usage.}
	\label{fig_efficient}
\end{figure}

@@

%% FIGURE 3
\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.8\textwidth]{fig/figure3.pdf}
	\caption{{\bf Static network model generators were modified to generate dynamic networks.}
		Three network models were used: Barabási–Albert, Erdős–Rényi, and Geometric. Step 0: a network is generated according to the network model and the given parameters. Step 1: the network is modified such that the result is as likely to have been generated by the network model. Step 2: The time for IncGraph to calculate the differences in graphlet counts is measured ($T_{IG}$). Step 3: The time for the non-incremental approach to calculate the graphlet counts of the new network is measured ($T_{NI}$). Steps 1 to 3 are repeated until all modifications generated at step 0 are processed, or until an execution time threshold has been reached.}
	\label{fig_method_speedup}
\end{figure}

@@

%% FIGURE 4
\begin{figure}[ht!]
	\centering
	\includegraphics[width=.9\linewidth]{fig/figure4.pdf}
	\caption{{\bf Predicted gene regulatory networks of model organisms are optimised to reduce the false positive rate.}
		A)~The number of redundant edges in each graphlet are counted. B) The network is optimised in order to obtain a lower redundancy over time. Two networks are shown, one before and one after the optimisation procedure. Edges coloured in red have been removed from the network after optimisation, green edges have been added. C) Starting from an empty network, the interactions are modified by iteratively evaluating the increase in redundancy of the next $k$ interactions, and adding the first edge for which its redundancy is less than the $90^\textrm{th}$ percentile redundancy.}
	\label{fig_method_reranking}
\end{figure}

@@

%% FIGURE 5
\begin{figure}[ht!]
	\centering
	\includegraphics[width=.8\textwidth]{fig/figure5.pdf}
	\caption{{\bf IncGraph is significantly faster than non-incremental approaches.}
		For small networks, the execution time of IncGraph $T_{IG}$ is already 50 times less than that of non-incremental approaches $T_{NI}$. This ratio increases even further for networks with higher numbers of nodes or higher average degrees.}
	\label{fig_speedup}
\end{figure}

@@

%% FIGURE 6
\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.5\textwidth]{fig/figure6.png}
	\caption{{\bf A simple graphlet-based scoring method improves predicted regulatory networks.}
		(A) The F1 score was calculated by calculating the harmonic mean of the AUROC and AUPR scores of the first 1000 interactions. (B) IncGraph is significantly faster than the non-incremental approach. Note that for each interaction added to the network, the graphlet counts of 100 putative interactions were evaluated.}
	\label{fig_reranking}
\end{figure}
